### 2025-07-29 submissions/02-jpam/tab01a-SumStatOverAll.tex
edits to mansucript

\begin{table}

\caption{CPS Summary Statistics \label{tab:sumstat1}}
\centering
\begin{threeparttable}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lc}
\toprule
Characteristic & All Sample 
N = 318,404\\
\midrule
Female & 0.49\\
Asian & 0.65\\
Age & 8.7 
(5.1)\\
College Graduate: 
 	 Father & 0.50\\
College Graduate: 
 	 Mother & 0.48\\
Total Family Income 
 	 (1999 dollars) & 78,763 
(80,171)\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\item[1] The sample includes children ages 17 and below who live in intact families. First-generation Asian immigrant children that were born in a Asian country. Native-born second-generation Asian immigrant children with at least one parent born in a Asian country. Finally, native-born third-generation Asian immigrant children with native-born parents and at least one grand parent born in a Asian country.
\item[2] Data source is the 2004-2021 Current Population Survey.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}
\centering
\caption{CPS Summary Statistics \label{tab:sumstat1}}
\centering
\begin{threeparttable}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{lc}
\toprule
Characteristic & All Sample N = 318,404\\
\midrule
Female & 0.49\\
Asian & 0.65\\
Age & 8.4 (5.1)\\
College Graduate:  	 Father & 0.52\\
College Graduate:  	 Mother & 0.52\\
Total Family Income  	 (1999 dollars) & 87,031 (84,797)\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\item[1] The sample includes children ages 17 and below who live in intact families. First-generation Asian immigrant children that were born in a Asian country. Native-born second-generation Asian immigrant children with at least one parent born in a Asian country. Finally, native-born third-generation Asian immigrant children with native-born parents and at least one grand parent born in a Asian country.
\item[2] Data source is the 2004-2021 Current Population Survey.
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2025-07-29 submissions/02-jpam/tab34-regression_tab_bygen_skin.tex
edits to mansucript

\begin{table}[!h]

\caption{Subjective Asian Child identity and Asian IAT: By Generation (State) \label{regtab-bygen-04}}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ $H_i$} & \specialcell{(2) \\ $H^1_i$} & \specialcell{(3) \\ $H^2_i$} & \specialcell{(4) \\ $H^3_i$}\\
\midrule
Implicit Bias & -0.62*** & -0.14* & -0.54*** & -0.57***\\
 & (0.09) & (0.08) & (0.08) & (0.10)\\
Female & -0.01* & -0.02*** & 0.00 & 0.00\\
 & (0.00) & (0.01) & (0.00) & (0.01)\\
College Graduate: Mother & 0.00 & -0.01 & 0.00 & 0.01\\
 & (0.01) & (0.01) & (0.01) & (0.01)\\
College Graduate: Father & 0.02*** & 0.02** & 0.01 & -0.01\\
 & (0.00) & (0.01) & (0.01) & (0.01)\\
\midrule
N & 268677 & 31586 & 167709 & 69382\\
Mean & 0.65 & 0.95 & 0.72 & 0.33\\
Year-Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} I include controls for sex, quartic age, parental education.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{2} Standard errors are clustered on the state level}\\
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}}
\end{table}

>>>>

\begin{table}[!h]
\centering\centering
\caption{Subjective Asian Child identity and Asian IAT: By Generation (State) \label{regtab-bygen-04}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ $H_i$} & \specialcell{(2) \\ $H^1_i$} & \specialcell{(3) \\ $H^2_i$} & \specialcell{(4) \\ $H^3_i$}\\
\midrule
Implicit Bias & -0.10*** & -0.06 & -0.09*** & -0.10**\\
 & (0.03) & (0.04) & (0.03) & (0.04)\\
Female & -0.01* & -0.01 & 0.00 & -0.01\\
 & (0.00) & (0.01) & (0.00) & (0.01)\\
College Graduate: Mother & 0.01 & -0.01 & 0.01 & 0.03\\
 & (0.01) & (0.01) & (0.01) & \vphantom{1} (0.02)\\
College Graduate: Father & 0.01** & 0.02** & 0.00 & -0.02\\
 & (0.01) & (0.01) & (0.01) & (0.02)\\
\midrule
N & 129078 & 15499 & 80137 & 33442\\
Mean & 0.65 & 0.96 & 0.73 & 0.31\\
Year-Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} I include controls for sex, quartic age, parental education.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{2} Standard errors are clustered on the state level}\\
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}}
\end{table}

### 2025-07-29 submissions/02-jpam/tab41a-marriage.tex
edits to mansucript

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Interethnic Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & $0.04$*** & $-0.01$ & $0.03$**\\
 & ($0.01$) & ($0.01$) & ($0.01$)\\
College Graduate: Wife & $0.04$*** & $0.04$*** & $0.05$***\\
 & ($0.00$) & ($0.01$) & \vphantom{1} ($0.00$)\\
College Graduate: Husband & $-0.01$* & $-0.01$ & $-0.02$***\\
 & ($0.00$) & ($0.01$) & ($0.00$)\\
\midrule
Observations & $69,800$ & $52,103$ & $60,214$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Relationship Between Bias and Interracial Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interracial} & \specialcell{(2) \\ Interracial} & \specialcell{(3) \\ Interracial}\\
\midrule
Bias & $0.04$*** & $-0.01$ & $0.03$**\\
 & ($0.01$) & ($0.01$) & ($0.01$)\\
College Graduate: Wife & $0.04$*** & $0.04$*** & $0.05$***\\
 & ($0.00$) & ($0.01$) & \vphantom{1} ($0.00$)\\
College Graduate: Husband & $-0.01$* & $-0.01$ & $-0.02$***\\
 & ($0.00$) & ($0.01$) & ($0.00$)\\
\midrule
Observations & $69,800$ & $52,103$ & $60,214$\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interracial}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}
